Order statistics and numerical optimization: the case of a single observation

### 2020-03-04 inst/skating_analysis.Rmd
copyediting

```{r}
skating_incorrect <- rank_likelihood(t(skating_table))
```

@@

```{r}
(skating_order <- ordertable_to_ranktable(skating_table))
```

@@

We can coerce from an order table to a likelihood function:

```{r}
head(ordertable2supp(skating_order))
```

>>>>

```{r,skatingwrong}
skating_incorrect <- rank_likelihood(t(skating_table))
```

@@

```{r,coercetoranktable}
(skating_order <- ordertable_to_ranktable(skating_table))
```

@@

We can convert an order table to a support function:

```{r,convertordertosupport}
head(ordertable2supp(skating_table))
```
